\documentclass{beamer}
\usetheme{Madrid}
%\usetheme{Goettingen}
\usefonttheme{serif}
\setbeamertemplate{navigation symbols}{}
\usefonttheme{structuresmallcapsserif}
\setbeamertemplate{footline}{}

\begin{document}
\begin{frame}{Verse 1}
 \huge{
    \centering
    Amazing Grace, how sweet the sound, \\
    that saved a wretch like me. \\
    I once was lost but now am found, \\
    was blind, but now, I see. \\
}
\end{frame}

\begin{frame}{Verse 2}
 \huge{
    \centering
    T'was Grace that taught my heart to fear, \\
    And Grace, my fears relieved. \\
    How precious did that Grace appear \\
    the hour I first believed. \\
}
\end{frame}

\begin{frame}{Verse 3}
 \huge{
    \centering
    Through many dangers, toils and snares \\
    I have already come. \\
    T'was Grace that brought us safe thus far \\
    and Grace will lead me home. \\
}
\end{frame}

\begin{frame}{Verse 4}
 \huge{
    \centering
    The Lord has promised good to me. \\
    His word my hope secures. \\
    He will my shield and portion be \\
    as long as life endures. \\
}
\end{frame}

\begin{frame}{Verse 5}
 \huge{
    \centering
    Yea, when this flesh and heart shall fail \\
    and mortal life shall cease, \\
    I shall possess within the veil \\
    a life of joy and peace. \\
}
\end{frame}

\begin{frame}{Verse 6}
 \huge{
    \centering
    When we've been here ten thousand years \\
    bright shining as the sun, \\
    We've no less days to sing God's praise \\
    than when we've first begun. \\
}
\end{frame}

\begin{frame}{Verse 7}
 \huge{
    \centering
    Amazing Grace, how sweet the sound, \\
    that saved a wretch like me. \\
    I once was lost but now am found, \\
    was blind, but now, I see. \\
}
\end{frame}
\end{document}
